---
title: "Introduction to the quickd3map package"
output:
  html_document:
    theme: spacelab
    highlight: tango
---
[quickd3map](http://github.com/zachcp/quickd3map) is an [htmlwidget](https://github.com/ramnathv/htmlwidgets)
 JavaScript/D3 chart library.

## Installation

`devtools::install_github("zachcp/quickd3map")`

## Usage

```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
options(dplyr.print_min = 4L, dplyr.print_max = 4L)
library(quickd3map)
```

The `quickd3map` pacakge is an `htmlwidget`^[http://www.htmlwidgets.org/] that is based on the `D3.js`^[http://d3js.org/] JavaScript library. Bubblemap is a near-clone of Mike Bostock's `symbol map`^[https://bost.ocks.org/mike/bubble-map/] and the HTMLWidget code is inspired by the `streamgraph package`^[http://hrbrmstr.github.io/streamgraph/]

## Making a Bubblemap

Bubblemaps place a circle at a specific geographic point and draws a circle whose radisu is the square root of the value. Bubblemaps dataframe and requires that the use specify latitute and longitude columns. 

Size can be controlled using the `sizecol` value or can be set to a single standard size using the `size` option.

```{r krbabies, message=FALSE, fig.width=9, fig.cap="'Kr-' names (1880-2013)"}
library(quickd3map)

bubblemap(data=uscities,
          latcol="Latitude",
          loncol="Longitude",
          namecol = "City",
          mapscale = 800,
          sizecol = "Area")
```


## Customize Size and Remove legend

```{r}
bubblemap(data     = uscities,
          latcol   = "Latitude",
          loncol   = "Longitude",
          namecol = "City",
          mapscale = 800,
          sizecol  = "Area",
          legend   = NULL)
```


## Control Size and Scale

```{r}
bubblemap(data      = uscities,
          latcol    = "Latitude",
          loncol    = "Longitude",
          namecol   = "City",
          mapscale  = 400,
          width     = 450,
          height    = 300,
          sizecol   = "Area",
          legend    = TRUE,
          maxrange  = 5)
```


## Other Maps

In addition to the US map there is also World Map data that allows points to be displayed on a world map.

```{r}
bubblemap(mapdata = "world", 
          data=uscities,
          latcol="Latitude",
          loncol="Longitude",
          mapscale = 100,
          sizecol = "Population",
          maxdomain = 1e6,
          maxrange = 5,
          legend =  T,
          namecol = "City"
)
```

